(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via D-D Neutron Generator\\ OR \\(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} at 2.76 MeV using a D-D Neutron Generator for Medical Isotope Studies

### 2016-12-23 First_np_Paper/first_np_paper.tex
Partially updated section 2.2 with first round edits, updated the foil holder illustration

Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a D-D neutron generator at the University of California Berkeley, seen in  \autoref{fig:hfng_a}. This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter. This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for D-D fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle \cite{Liskien_Paulsen_1973}. Within the center of the target (at 8 mm from the D-D reaction surface), samples may be inserted prior to  HFNG startup. \autoref{fig:hfng_b} displays the target setup. At the time of the presented experiments, the machine operated under nominal conditions of a 100 kV deuterium beam extracted at 1.5 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.

\comment{Karl: Comment or question primarily to Lee: Is it conventional to put photographs of equipment in PRC? I’m not sure it is; yes certainly for NIM, but not sure about PRC.}

@@

For the measurement of the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section, a natural abundance commercial (Goodfellow) zinc foil was cut down to 1-cm in diameter and used as a target; similarly a natural abundance commercial (Goodfellow) titanium foil was used as target for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} reaction. Target foils of 1-cm diameter and 1-mm thickness were co-loaded with a natural-abundance Indium foil of 1-cm diameter and 0.5-mm thickness in a recess cut into a 2-mm thin polyethylene holder, as seen in \autoref{fig:main_holders}. Prior to loading, each foil was washed with isopropanol and dried, to remove any trace oils or residue which could become activated during irradiation. The recorded physical characteristics of each foil for the various irradiations are recorded in \autoref{tab:foil_specs}. In each experiment, the co-loaded foils were subjected to 3 hour irradiation at nominal operating conditions of 1.3 mA and 100 kV, to saturate the induced Indium isomer activity.

>>>>

Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a D-D neutron generator at the University of California, Berkeley, seen in  \autoref{fig:hfng_a}. This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter. This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for D-D fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle \cite{Liskien_Paulsen_1973}. Within the center of the target (at 8 mm from the D-D reaction surface), samples may be inserted prior to  HFNG startup. \autoref{fig:hfng_b} displays the target setup. At the time of the presented experiments, the machine operated under nominal conditions of a 100 kV deuterium beam extracted at 1.5 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.

\comment{Karl: Comment or question primarily to Lee: Is it conventional to put photographs of equipment in PRC? I'm not sure it is; yes certainly for NIM, but not sure about PRC.}

@@

For the measurement of the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section, a natural abundance commercial zinc foil of 1 cm diameter and 1 mm thickness was used as a target; a natural abundance titanium foil of the same dimensions was used as a target for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} reaction. For each run the target foils were co-loaded with a natural abundance Indium foil of 1 cm diameter and 0.5 mm thickness in a recess cut into a 2-mm thin polyethylene holder, as seen in \autoref{fig:main_holders}. Prior to loading, each foil was washed with isopropanol and dried, to remove any trace oils or residue that could become activated during irradiation.  \autoref{tab:foil_specs} records physical characteristics of each foil for the various irradiations. In each experiment, the co-loaded foils were irradiated for 3 hours at nominal operating conditions of 1.3 mA and 100 kV, to saturate the induced Indium isomer activity.
